Breeding bird indicators

### 2023-10-23 NDVI_seminat.Rmd
more prallel-comit-issues fixed

```{r setup, include=FALSE}
library(downloader)
library(data.table)
library(lubridate)
library(sf)
library(plyr)
library(stringr)
library(tidyverse)
library(RColorBrewer)
library("gridExtra")
library(ggridges)
library(tmap)
library(tmaptools)
library(betareg)
library(StepBeta)
library(glmmTMB)
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
```

@@

In addition, there are 10 T31s, 78 T32s, 15 T33s, 59 T34s, and 1 T40
that are not assigned to any region.

>>>>

```{r setup, include=FALSE}
library(downloader)
library(data.table)
library(lubridate)
library(sf)
library(plyr)
library(stringr)
library(tidyverse)
library(RColorBrewer)
library("gridExtra")
library(ggridges)
library(tmap)
library(tmaptools)
library(betareg)
library(StepBeta)
library(glmmTMB)
library(knitr)
library(flextable)
knitr::opts_chunk$set(echo = TRUE)
```

@@

In addition, there are 10 T31s, 78 T32s, 15 T33s, 59 T34s, and 1 T40
that are not assigned to any region. (These polygons likely lie in water and thus outside of the regional polygons due to imprecise coordinates from the mapping device).

### 2023-10-23 alien_species.Rmd

```{r setup, include=FALSE}
library(knitr)
library(tidyverse)
library(sf)
library(tmap)
library(ggpubr)
library(DT)
library(units)
library(eaTools)
library(tibble)
library(stars)
library(gdalUtilities)
knitr::opts_chunk$set(echo = TRUE)

@@

```{r alien-precentageplot, fig.height=5, fig.width=8, fig.cap="Relative frequency plot showing the distribution of polygons with different indicator values."}
ggplot(corrCheck, aes(x = factor(infrastructureIndex), fill = factor(round(i_2020,2))))+
  geom_bar(position="fill")+
  theme_bw(base_size = 12)+
  guides(fill = guide_legend("Alien species indicator"))+
  ylab("Fraction of data points")+
  xlab("HIF")+
  scale_fill_brewer(palette = "RdYlGn")+
  facet_wrap(.~hovedøkosystem)
```

@@

>>>>

```{r setup, include=FALSE}
library(knitr)
library(tidyverse)
library(sf)
library(tmap)
library(ggpubr)
library(DT)
library(units)
library(eaTools)
library(tibble)
library(stars)
library(gdalUtilities)
library(flextable)
knitr::opts_chunk$set(echo = TRUE)

@@

```{r alien-precentageplot, fig.cap="Relative frequency plot showing the distribution of polygons with different indicator values."}
ggplot(corrCheck, aes(x = factor(infrastructureIndex), fill = factor(round(i_2020,2))))+
  geom_bar(position="fill")+
  theme_bw(base_size = 12)+
  guides(fill = guide_legend("Alien species indicator"))+
  ylab("Fraction of data points")+
  xlab("HIF")+
  scale_fill_brewer(palette = "RdYlGn")+
  facet_wrap(.~hovedøkosystem)
```

@@

```{r, include=FALSE, eval=FALSE}
# Figure for the report
corrCheck  %>%
  mutate(hovedøkosystem = forcats::fct_recode(factor(hovedøkosystem), "Naturlig åpne" = "naturligÅpneOmråderUnderSkoggrensa",
                      "Semi-naturlig mark" = "semi-naturligMark",
                      "Våtmark" = "våtmark")) %>%
ggplot(aes(x = factor(infrastructureIndex), fill = factor(round(i_2020,2))))+
  geom_bar(position="fill")+
  theme_bw(base_size = 12)+
  guides(fill = guide_legend("Indikatorverdi"))+
  ylab("Andel av datapunkter")+
  xlab("Infrastrukturindeksen (kategorisk versjon)")+
  scale_fill_brewer(palette = "RdYlGn")+
  facet_wrap(.~hovedøkosystem)

### 2023-10-23 functional_plant_indicators_wetland.Rmd

# Functional Plant Indicators - Wetlands {#Functional-plant-indicators-wetland}

@@

<!-- Load all you dependencies here -->
```{r setup, include=FALSE, warning=F, message=F}
library(sf)
library(plyr)
library(tidyverse)
library(RColorBrewer)
library(gridExtra) 
library(ggridges)
library(tmap)
library(tmaptools)
library(raster)
library(stars)
library(knitr)
library(kableExtra)
library(betareg)
library(glmmTMB)
knitr::opts_chunk$set(echo = TRUE)
```

>>>>

# Functional Plant Indicators - Wetlands {#functional-plant-indicators-wetland}

@@

<!-- Load all you dependencies here -->
```{r setup, include=FALSE, warning=F, message=F}
library(sf)
library(plyr)
library(tidyverse)
library(RColorBrewer)
library(gridExtra) 
library(ggridges)
library(tmap)
library(tmaptools)
library(raster)
library(stars)
library(knitr)
library(kableExtra)
library(betareg)
library(glmmTMB)
library(flextable)

knitr::opts_chunk$set(echo = TRUE)
```

### 2023-10-23 medianSummerTemperature.Rmd

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
library(stringr, lib.loc = "/usr/lib/R/site-library")
library(tidyverse, lib.loc = "/usr/local/lib/R/site-library")
#library(tidyverse)
library(stars)
library(sf)
library(tmap)
library(lubridate)
library(ggpubr)
library(microbenchmark)
library(tictoc)
library(ncmeta)
library(parallel)
library(exactextractr)
library(data.table)
library(terra)
dir <- substr(getwd(), 1,2)
pData <- ifelse(dir == "C:", 
  "P:/41201785_okologisk_tilstand_2022_2023/data/",
  "/data/P-Prosjekter2/41201785_okologisk_tilstand_2022_2023/data/")
```

@@

```{r, echo=F}
metaData <- data.frame(Ecosystem,
                       "Økologisk egenskap" = Egenskap,
                       "ECT class" = ECT)
knitr::kable(metaData)
```

>>>>

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(stars)
library(sf)
library(tmap)
library(lubridate)
library(ggpubr)
library(microbenchmark)
library(tictoc)
library(ncmeta)
library(parallel)
library(exactextractr)
library(data.table)
library(terra)
library(flextable)
dir <- substr(getwd(), 1,2)
pData <- ifelse(dir == "C:", 
  "P:/41201785_okologisk_tilstand_2022_2023/data/",
  "/data/P-Prosjekter2/41201785_okologisk_tilstand_2022_2023/data/")
```

@@

```{r, echo=F}
metaData <- data.frame(Ecosystem,
                       "Økologisk egenskap" = Egenskap,
                       "ECT class" = ECT,
                       check.names = F)
flextable(metaData) %>%
  bg(bg = "lightblue", part="header") %>%
  theme_vanilla() %>%
  set_table_properties(layout = "autofit")
